%
\subsection{The hardness amplification proof for partitioned domains}
\label{st:amplification_proof}
In this section we prove Lemma \ref{lemma:sec_amp_for_p_hash} which in the great extent bases on~\cite{holenstein2011general}.

We need to introduce some additional algorithms and circuits before giving the proof of Lemma \ref{lemma:sec_amp_for_p_hash} .
The following code listing depicts the algorithm $\widetilde{\Gen}$.
The algorithm $\EstimateSurplus$ and the circuits $\widetilde{D}$, $\widetilde{C}' := (C_1',\widetilde{C}_2')$ used by $\widetilde{Gen}$ are presented on the succeeding code excerpts.
Intuitively, the algorithm $\EstimateSurplus$ returns an estimate of an advantage of $\widetilde{C}$
over the algorithm that solves each puzzle independently with probability $\delta$
where the randomness used to generate a puzzle on the first position is fixed to $\pi^*$
and the fact of solving this puzzle is disregarded.
The circuit $\widetilde{D}$ outputs a solution $(q,y)$ for a puzzle defined by~$P^{(1)}$.
The circuit $\widetilde{C}'$ is a solver for the $(k\!-\!1)$-wise direct product of puzzles that outputs an answer $(q, y_1, \dotsc, y_{k-1})$.
%
\begin{codeblock}
  \textbf{Algorithm} $\widetilde{\Gen}^{P^{(1)}, \widetilde{C}, g, \mathit{hash}}(\epsilon, \delta, n, k)$
  \medskip \hrule
  \textbf{Oracle:} A problem poser $P^{(1)}$, a solver $\widetilde{C}$ for $P^{(g)}$, functions $g: \{0,1\}^{k} \rightarrow \{0,1\}$, $hash:\cQ \rightarrow \{0,1, \dots, 2(h + v) - 1\}$. \\
  \textbf{Input:}  Parameters $\epsilon$, $\delta$, $n$, $k$.\\
  \textbf{Output:} A circuit $\widetilde{D}$.
  \medskip\hrule
  \For $i:=1$ \To $\frac{6k}{\epsilon}n$ \Do \\
  \IndI $\pi^* \xleftarrow{\$} \{0,1\}^{n}$\\
  \IndI $\widetilde{S}_{\pi^*,0} := \text{EstimateSurplus}^{P^{(1)},  \widetilde{C}, g, hash}(\pi^*, 0, k, \epsilon, \delta,n)$\\
  \IndI $\widetilde{S}_{\pi^*,1} := \text{EstimateSurplus}^{P^{(1)},  \widetilde{C}, g, hash}(\pi^*, 1, k, \epsilon, \delta,n)$\\
  \IndI \If $ \exists b \in \{0,1\}: \widetilde{S}_{\pi^*,b} \geq (1 - \frac{3}{4k}) \epsilon$ \Then \\
  \IndII Let $C_1'$ have oracle access to $\widetilde{C}$ and have hard-coded $\pi^*$. \\
  \IndII Let $\widetilde{C}_2'$ have oracle access to $\widetilde{C}$ and have hard-coded $\pi^*$. \\
  \IndII $\widetilde{C}' := (C_1', \widetilde{C}_2')$ \\
  \IndII $g'(b_2, \dots, b_k) := g(b, b_2, \dots, b_k)$\\
  \IndII\Return $\widetilde{Gen}^{P^{(1)}, \widetilde{C}', g', hash}(\epsilon, \delta, n, k-1)$ \\
  \textit{// all estimates are lower than $(1-\frac{3}{4k})\varepsilon$}\\
  \Return $\widetilde{D}^{P^{(1)}, \widetilde{C}, hash, g}$
\end{codeblock}

The algorithm $\EstimateSurplus$ uses procedures $\EstimateFunctionProbability$ and $\EvalutePuzzles$.
We state them first before $\EstimateSurplus$.

We are interested in the probability that for $u \leftarrow \mu_{\delta}^k$ and $b \in \{0,1\}$ we have $g(b,u_2, \dotsc, u_k) = 1$.
The estimate of this probability is calculated by $\EstimateFunctionProbability$.
%
\begin{codeblock}
  \textbf{Algorithm} $\text{EstimateFunctionProbability}^{g}(b, k, \epsilon, \delta, n)$
  \medskip\hrule
  \textbf{Oracle:} A function $g : \{0,1\}^{k} \rightarrow \{0,1\}$.\\
  \textbf{Input:} A bit $b \in \{0,1\}$, parameters $k$, $\epsilon$, $\delta$, $n$. \\
  \textbf{Output:} An estimate $\widetilde{g}_b$ of $\Pr_{u \leftarrow \mu_{\delta}^{k}}[g(b,u_2, \dotsc, u_k) = 1]$.
  \medskip\hrule
  \For $i:=1$ \To $N := \frac{64k^2}{\epsilon^2} n$ \Do \\
  \IndI $u \leftarrow \mu_{\delta}^{k}$ \\
  \IndI $g_i := g(b, u_2, \dotsc, u_k)$ \\
  \Return $\frac{1}{N} \sum_{i=1}^{N} g_i$
\end{codeblock}
%
% For fixed $\pi^{(k)}$, $\rho$, and $hash$ we say that the circuit $\widetilde{C} := (C_1, \widetilde{C}_2)$ \textit{succeeds on the $i$-th coordinate}
% if for $x := \langle P^{(g)}(\pi^{(k)}), C_1(\rho) \rangle_{\mathit{trans}}$, $(\Gamma_V^{(g)}, \Gamma_H^{(k)}) := \langle P^{(g)}(\pi), C_1(\rho) \rangle_{P^{(g)}}$ and
% $(q, y^{(k)}) := \widetilde{C}_2(x, \rho)$ we have
% \begin{align*}
%   \Gamma_V^i(q, y_i) = 1.
% \end{align*}
%
\begin{lemma}
  \label{lemma:estimate_of_g}
  The algorithm $\text{EstimateFunctionProbability}^{g}(b, k, \epsilon, \delta, n)$ outputs an estimate $\widetilde{g}_b$
  such that $| \widetilde{g}_b - \Pr_{u \leftarrow \mu_{\delta}^{k}}\left[g(b,u_2, \dots, u_k) = 1\right] | \leq \frac{\epsilon}{8k}$ almost surely.
\end{lemma}
%
\begin{proof}
We fix the notation as in the code listing of the algorithm EstimateFunctionProbability.
Let us define independent and identically distributed binary random variables $K_1, K_2, \dots, K_N$
such that for each $1 \leq i \leq N$ the random variable $K_i$ takes value $g_i$. We use the Chernoff bound to obtain
\begin{align*}
  &\Pr \Bigl[ \Bigl| \widetilde{g}_b - \Pr_{u \leftarrow \mu_{\delta}^{k}}\left[g(b,u_2, \dots, u_k) = 1\right] \Bigr| \geq \frac{\epsilon}{8k} \Bigr]\\
  &\IndII = \Pr \Bigl[\Bigl|\Bigl(\frac{1}{N} \sum_{i=1}^N K_i \Bigr) - \mathbb{E}_{u \leftarrow \mu_{\delta}^k}[g(b,u_2, \dots, u_k)]\Bigr|
    \geq \frac{\epsilon}{8k} \Bigr] \leq 2 \cdot e^{-n/3}.
\end{align*}
\end{proof}
%
The algorithm $\text{EvalutePuzzles}^{P^{(1)}, \widetilde{C}, \hash}(\pi^{(k)}, \rho, n, k)$
evaluates which of the $k$ puzzles of the $k$-wise direct product of $P^{(1)}$ are solved successfully by $\widetilde{C}(\rho) := (C_1,\widetilde{C}_2)(\rho)$.
To decide whether the $i$-th puzzle of the $k$-wise direct product is solved successfully we need to gain access to the verification circuit
for the puzzle generated in the $i$-th round of the interaction between $P^{(g)}$ and $\widetilde{C}$.
Therefore, the algorithm EvalutePuzzles runs $k$ times $P^{(1)}(\pi_i)$ to simulate the interaction with
$C_1(\rho)$.

Let us introduce the additional notation.
We write $\langle P^{(1)}(\pi_i), C_1(\rho)\rangle^i$ to denote the $i$-th round of the sequential interaction.
Let $\langle P^{(1)}(\pi_i), C_1(\rho)\rangle^i_{P^{(1)}}$ be the output of $P^{(1)}(\pi_i)$ in the $i$-th round.
Finally, we write $\langle P^{(1)}(\pi_i), C_1(\rho)\rangle^i_{\mathit{trans}}$ to denote the transcript of communication in the $i$-th round.
We note that the $i$-th round of the interaction between $P^{(1)}$ and $C_1$ is well defined if all previous rounds have been executed before.

For simplicity of the notation in the code excerpts of circuits EvalutePuzzles, $\widetilde{C}'_2$, $\widetilde{D}_2$ we omit superscripts of some oracles.
Exemplary, in the code listing of EvalutePuzzles for $\widetilde{C}_2^{\Gamma_H^{(k)}, C, \hash}$ we omit $C$ in the superscript and instead write $\widetilde{C}_2^{\Gamma_H^{(k)}, \hash}$.
We make sure that it is clear from the context which oracles are used.

\begin{codeblock}
  \textbf{Algorithm} $\EvalutePuzzles^{P^{(1)}, \widetilde{C}, \hash}(\pi^{(k)}, \rho, n, k)$
  \medskip \hrule
  \textbf{Oracle:}  A problem poser $P^{(1)}$, a solver circuit $\widetilde{C} := (C_1, \widetilde{C}_2)$ for $P^{(g)}$,\\
  \IndII a function $hash : \cQ \rightarrow \{0,1,\dots, 2(h+v)-1\}$.\\
  \textbf{Input:} Bitstrings $\pi^{(k)} \in \{0,1\}^{kn}$, $\rho \in \{0,1\}^{*}$, parameters $n$, $k$.\\
  \textbf{Output}: A tuple $(c_1, \dots, c_k) \in \{0,1\}^{k}$.
  \medskip\hrule
  %
  \For $i:=1$ \To $k$ \Do \IndII \textit{//simulate $k$ rounds of interaction} \\
  \IndI $(\Gamma_V^{i}, \Gamma_H^{i}) := \langle P^{(1)}(\pi_i), C_1(\rho) \rangle_{P^{(1)}}^i$\\
  \IndI $x_i := \langle P^{(1)}(\pi_i), C_1(\rho) \rangle^i_{\mathit{trans}}$ \\
  $x := (x_1, \dots, x_k)$ \\
  $\Gamma_H^{(k)} := (\Gamma_H^1, \dotsc, \Gamma_H^k)$ \\
  $(q, y_1, \dots, y_k) := \widetilde{C}_2^{\Gamma_H^{(k)}, hash} (x, \rho)$ \\
  \If $(q, y_1, \dots, y_k) = \bot$ \Then \\
  \IndI \Return $(0, \dotsc, 0)$ \\
  $(c_1, \dotsc, c_k) := (\Gamma_V^{1}(q, y_1), \dotsc, \Gamma_V^{k}(q, y_k))$\\
  \Return $(c_1, \dotsc, c_k)$
\end{codeblock}
%
All puzzles are generated  by $\EvalutePuzzles$. Thus, the algorithm can answer all queries of $\widetilde{C}_2$.

We are interested in the success probability of $\widetilde{C}$ with the bitstring $\pi_1$ fixed to $\pi^*$ where
the fact whether $\widetilde{C}$ succeeds in solving the puzzle placed on the first position is neglected
and instead $b \in \{0,1\}$ is used. More formally, we introduce the notion of a surplus $S_{\pi^*, b}$ defined as
\begin{align}
  \label{eq:s_pi_b}
S_{\pi^*, b} = \underset{\pi^{(k)}, \rho}{\Pr}\left[g(b, c_2, \dots, c_k) = 1 \mid \pi_1 = \pi^*\right] - \underset{u \leftarrow \mu^{k}_{\delta}}{\Pr}\left[g(b, u_2, \dots, u_k) = 1\right],
\end{align}
where $(c_2, c_3, \dotsc, c_k)$ is obtained as in EvalutePuzzles.

The algorithm $\EstimateSurplus$ returns an estimate $\widetilde{S}_{\pi^*, b}$ for $S_{\pi^*, b}$.
%
\begin{codeblock}
  \textbf{Algorithm} $\EstimateSurplus^{P^{(1)}, \widetilde{C}, g, \hash}(\pi^*, b, k, \epsilon, \delta, n)$
  \medskip\hrule
  \textbf{Oracle:} A problem poser $P^{(1)}$, a circuit $\widetilde{C}$ for $P^{(g)}$, functions \\
  \IndII $g: \{0,1\}^{k} \rightarrow \{0,1\}$ and  $\hash : \cQ \rightarrow \{0,1,\dots, 2(h+v)-1\}$.\\
  \textbf{Input:} A bistring $\pi^* \in \{0,1\}^{n}$, a bit $b \in \{0,1\}$, parameters $k$, $\epsilon$, $\delta$, $n$.\\
  \textbf{Output:} An estimate $\widetilde{S}_{\pi^*, b}$ for $S_{\pi^*, b}$.
  \medskip\hrule
  \For $i:=1$ \To $N := \frac{64k^2}{\epsilon^2}n$ \Do \\
  \IndI $(\pi_{2}, \dots, \pi_k) \xleftarrow{\$} \{0,1\}^{(k-1)n}$\\
  \IndI $\rho \xleftarrow{\$} \{0,1\}^{*}$\\
  \IndI $(c_1, \dots, c_k) := \text{EvalutePuzzles}^{P^{(1)}, \widetilde{C}, \hash}((\pi^*, \pi_2, \dots, \pi_k), \rho, n, k)$\\
  \IndI $\widetilde{s}_{\pi^*,b}^i := g(b, c_{2}, \dots, c_k)$\\
  $\widetilde{g}_b := \text{EstimateFunctionProbability}^{g}(b, k, \epsilon, \delta, n)$ \\
  \textbf{return} $\Bigl(\frac{1}{N} \sum_{i=1}^N \widetilde{s}_{\pi^*,b}^i \Bigr) - \widetilde{g}_b$
\end{codeblock}
%
\begin{lemma}
  \label{lemma:surplus_estimate}
The estimate $\widetilde{S}_{\pi^*,b}$ returned by EstimateSurplus differs from $S_{\pi^*, b}$ by at most $\frac{\epsilon}{4k}$ almost surely.
\end{lemma}

\begin{proof}
We use the union bound and similar argument as in Lemma \ref{lemma:estimate_of_g}
which yields that $\frac{1}{N} \sum_{i=1}^{N} \widetilde{s}_{\pi^*,b}^i$ differs from
$\mathbb{E}[g(b, c_2, \dots, c_k)]$ by at most $\frac{\epsilon}{8k}$ almost surely. Together, with Lemma $\ref{lemma:estimate_of_g}$ we conclude that the surplus estimate
returned by EstimateSurplus differs from $S_{\pi^*,b}$ by at most $\frac{\epsilon}{4k}$ with probability at least $1 - 2e^{-n}$.
\end{proof}
%
We define the following circuit $\widetilde{C}' = (C_1', \widetilde{C}_2')$ for the $(k-1)$-wise direct product of $P^{(1)}$.
Loosely speaking, in the recursive calls of $\widetilde{\Gen}$ we fix the randomness used to generate the puzzle on the first position.
The circuit $\widetilde{C}'$ uses the circuit $\widetilde{C}$ for the $k$-wise direct product where
the first puzzle is generated internally using the fixed randomness.

\begin{codeblock}
  \textbf{Circuit} $C_1'^{\widetilde{C}, P^{(1)}}(\rho)$
  \medskip \hrule
  \textbf{Oracle:} A solver circuit $\widetilde{C} = (C_1, \widetilde{C}_2)$ for $P^{(g)}$, a poser $P^{(1)}$. \\
  \textbf{Input:}  A bitstring $\rho \in \{0,1\}^{*}$. \\
  \textbf{Hard-coded:} A bitstring $\pi^* \in \{0,1\}^{n}$.
  \medskip\hrule
  Simulate $\langle P^{(1)}(\pi^*), C_1(\rho)\rangle^1$ \\
  Use $C_1(\rho)$ for the remaining $k-1$ rounds of interaction.
\end{codeblock}
%
\begin{codeblock}
  \textbf{Circuit} $\widetilde{C}_2'^{\Gamma_H^{(k-1)}, \widetilde{C}, \hash}(x^{(k-1)}, \rho)$
  \medskip \hrule
  \textbf{Oracle:} A hint oracle $\Gamma_H^{(k-1)} := (\Gamma_H^{2}, \dots, \Gamma_H^{k})$,\\
  \IndII a solver circuit $\widetilde{C} = (C_1, \widetilde{C}_2)$ for $P^{(g)}$, \\
  \IndII a function $\hash: \cQ \rightarrow \{0,1,\dots, 2(h+v)-1\}$. \\
  \textbf{Input:}  A transcript of $k-1$ rounds of interaction \\
  \IndII $x^{(k-1)} := (x_2, \dotsc, x_{k}) \in \{0,1\}^{*}$, a bitstring $\rho \in \{0,1\}^{*}$.\\
  \textbf{Hard-coded:} A bitstring $\pi^* \in \{0,1\}^{n}$. \\
  \textbf{Output:} A tuple $(q, y_2, \dots, y_k)$.
  \medskip\hrule
  Simulate $\langle P^{(1)}(\pi^*), C_1(\rho) \rangle^{1}$ \\
  \IndI $(\Gamma_H^*, \Gamma_V^*) := \langle P^{(1)}(\pi^*), C_1(\rho) \rangle^{1}_{P^{(1)}}$ \\
  \IndI $x^* := \langle P^{(1)}(\pi^*), C_1(\rho) \rangle^{1}_{\mathit{trans}}$ \\
  $\Gamma_H^{(k)} := (\Gamma_H^*, \Gamma_H^{2}, \dots, \Gamma_H^{k})$ \\
  $x^{(k)} := (x^*, x_2, \dots, x_{k})$ \\
  $(q, y_1, \dots, y_k) := \widetilde{C}_2^{\Gamma_H^{(k)}, \mathit{hash}}(x^{(k)}, \rho)$ \\
  \Return $(q, y_2, \dots, y_k)$
\end{codeblock}
%
Finally, we define the solver circuit $\widetilde{D} = (D_1, \widetilde{D}_2)$ for $P^{(1)}$.
%
\begin{codeblock}
  \textbf{Circuit} $D_1^{\widetilde{C}}(r)$
  \medskip \hrule
  \textbf{Oracle:} A solver circuit $\widetilde{C} = (C_1, \widetilde{C}_2)$ for $P^{(g)}$.\\
  \textbf{Input:} A pair $r := (\rho, \sigma)$ where $ \rho \in \{0,1\}^{*}$ and $\sigma \in \{0,1\}^{*}$.
  \medskip\hrule
  Interact with the problem poser $\langle P^{(1)}, C_1(\rho) \rangle^1$. \\
  Let $x^* := \langle P^{(1)}, C_1(\rho) \rangle^1_{\mathit{trans}}$.
\end{codeblock}
%
\begin{codeblock}
  \textbf{Circuit} $\widetilde{D}_2^{P^{(1)}, \widetilde{C}, \hash, g,  \Gamma_H}(x^*, r)$
  \medskip \hrule
  \textbf{Oracle:} A poser $P^{(1)}$, a solver circuit $\widetilde{C} = (C_1, \widetilde{C}_2)$ for $P^{(g)}$, \\
  \IndII functions $hash : \cQ \rightarrow \{0,1, \dots, 2(h+v)-1\}$, $g:\{0,1\}^k \rightarrow \{0,1\}$, \\
  \IndII a hint circuit $\Gamma_H$ for $P^{(1)}$. \\
  \textbf{Input:} A communiation transcript $x^* \in \{0,1\}^{*}$, a bitstring $r := (\rho, \sigma)$ \\
  \IndII where $\rho \in \{0,1\}^{*}$ and $\sigma \in \{0,1\}^{*}$\\
  \textbf{Output}: A pair $(q, y^*)$.
  \medskip \hrule
  \For at most $\frac{6k}{\epsilon} \log(\frac{6k}{\epsilon})$ iterations \Do \\
  \IndI $(\pi_2, \dots, \pi_k) \leftarrow$ read next $(k-1)\cdot n$ bits from $\sigma$ \\
  \IndI Use $x^*$ to simulate the first round of interaction of $C_1(\rho)$ \\
  \IndI with the problem poser $P^{(1)}$.\\
  \IndI \For $i:=2$ \To $k$ \Do \\
  \IndII \Run $\langle P^{(1)}(\pi_i), C_1(\rho)\rangle^i$ \\
  \IndIII $(\Gamma_V^{i}, \Gamma_H^{i}) := \langle P^{(1)}(\pi_i), C_1(\rho) \rangle^i_{P^{(1)}}$ \\
  \IndIII $x_i := \langle P^{(1)}(\pi_i), C_1(\rho) \rangle^i_{\mathit{trans}}$ \\
  \IndI $\Gamma_H^{(k)}(q) := (\Gamma_H(q), \Gamma_H^{2}(q), \dots, \Gamma_H^{k}(q))$ \\
  \IndI $(q, y^*, y_2, \dots, y_k) := \widetilde{C}_2^{\Gamma_H^{(k)}, \hash}((x^*, x_2, \dotsc, x_k), \rho)$\\
  \IndI $(c_2, \dots, c_k) := (\Gamma_V^2(q, y_2), \dotsc, \Gamma_V^{k}(q, y_k))$ \\
  \IndI \If $g(1, c_{2}, \dots, c_k) = 1$ \And $g(0,c_{2}, \dots, c_k) = 0$ \Then \\
  \IndII \Return $(q, y^*)$ \\
  \Return $\bot$
%
\end{codeblock}
%
%
\begin{proof}[Proof of Lemma \ref{lemma:sec_amp_for_p_hash}]
First, let us consider the case where $k=1$. The function $g: \{0,1\} \rightarrow \{0,1\}$ is either the identity or a constant function.
In the latter case, when $g$ is a constant function, Lemma \ref{lemma:sec_amp_for_p_hash} is vacuously true.
If $g$ is the identity function, then the circuit $\widetilde{D}$ directly uses $\widetilde{C}$ to find a solution.
From the assumptions of Lemma \ref{lemma:sec_amp_for_p_hash} it follows that $\widetilde{C}$ succeeds with probability at least
$\delta + \epsilon$. Hence, $\widetilde{D}$ trivially satisfies Lemma~\ref{lemma:sec_amp_for_p_hash}.

For the general case, we consider two possibilities.
Namely, either $\widetilde{\Gen}$ in one of the iterations finds an estimate such that $\widetilde{S}_{\pi, b} \geq (1-\frac{3}{4k})\epsilon$ and recurses,
or in all iterations it fails and outputs the circuit~$\widetilde{D}$.

If it is possible to find an estimate with the high surplus, then we introduce a~new monotone function $g': \{0,1\}^{k-1} \rightarrow \{0,1\}$
such that $g'(b_2, \dots, b_k) := g(b, b_2, \dots, b_k)$ and a new circuit $\widetilde{C}' = (C_1', \widetilde{C}_2')$
with oracle access to $\widetilde{C}$. We apply Lemma \ref{lemma:surplus_estimate} and conclude that almost surely it holds
\begin{align*}
S_{\pi^*,b} \geq \widetilde{S}_{\pi^*, b} - \frac{\epsilon}{4k} \geq \Bigl(1 - \frac{1}{k}\Bigr)\epsilon.
\end{align*}
It follows that $\widetilde{C}'$ succeeds in solving the $(k\!-\!1)$--wise direct product of puzzles with probability at least
\begin{align*}
\Pr_{u \leftarrow \mu^{(k-1)}_{\delta}}[g'(u_1,\dots, u_{k-1} )] + \Bigl(1 - \frac{1}{k}\Bigr)\epsilon.
\end{align*}
In this case $\widetilde{C}'$ satisfies the conditions of Lemma \ref{lemma:sec_amp_for_p_hash} for the $(k\!-\!1)$-wise direct product of puzzles.
The recursive call to $\widetilde{\Gen}$, which has oracle access to $g'$ and $\widetilde{C}$, returns $\widetilde{D} = (D_1, \widetilde{D}_2)$
that with high probability satisfies
\begin{align}
  \underset{
    \mathclap{
      \substack{
        \pi, \rho \\
        x := \langle P^{(1)}(\pi), D_1^{\widetilde{C}}(\rho) \rangle_{\mathit{trans}} \\
        (\Gamma_H, \Gamma_V) := \langle P^{(1)}(\pi), D_1^{\widetilde{C}}(\rho) \rangle_{P^{(1)}}}}}
  {\Pr}\Big[\Gamma_V\big(\widetilde{D}_2^{P^{(1)}, \widetilde{C}, \hash, g, \Gamma_H}(x, \rho)) = 1\Big]
  &\geq \delta + \Bigl(1 - \frac{1}{k}\Bigr)\frac{\epsilon}{6(k-1)} \notag\\
  &= \delta + \frac{\epsilon}{6k}.
\end{align}
%
Let us bring our attention to the case where none of the estimates is greater than $(1-\frac{3}{4k})\epsilon$.
If all surpluses $S_{\pi,0}$ and $S_{\pi,1}$ were lower than $(1-\frac{1}{k})\epsilon$, then it would mean that $\widetilde{C}$
does not succeed on the remaining $k-1$ puzzles with much higher probability than an algorithm that solves each puzzle
independently with success probability $\delta$. However, from the assumptions of Lemma~\ref{lemma:sec_amp_for_p_hash}
we know that on all $k$ puzzles the success probability of $\widetilde{C}$ is higher.
Hence, we suspect that the first puzzle is correctly solved unusually often.
It remains to show that the fact that $\widetilde{\Gen}$ fails to find a surplus estimate that is large implies that
with high probability there are only few surpluses greater than $(1-\frac{1}{k})\epsilon$ and their influence
can be neglected. Additionally, we have to show that the circuit $\widetilde{D}$ outputs an answer almost surely.

The proof in this case requires lengthly probability manipulations.
In Appendix \ref{st:proofSimAssm} we give a shorter proof under the simplifying assumptions
that the circuit $\widetilde{D}$ always outputs an answer and all surpluses are low.

We fix the notation as in the code listing of $\widetilde{D}_2$.
Let us consider a single iteration of the outer loop of $\widetilde{D}_2$ where values $\pi_2, \dotsc, \pi_k$ are fixed.
We write $\pi_1$ to denote the randomness used by the problem poser to generate the input puzzle.
Furthermore, we define $c_1 := \Gamma_V(q,y_1)$ where $\Gamma_V$ is the verification circuit generated
by $P^{(1)}(\pi_1)$ in the first phase when interacting with $D_1$.
We write $c := (c_1, c_2, \dotsc, c_k)$, and for $b \in \{0,1\}$ we define a set
\begin{align*}
\cG_{b}~:=~\big\{(b_1, b_2, \dots, b_k) : g(b, b_2, \dots, b_k) = 1 \big\}.
\end{align*}
Using this notation we express
\begin{align}
  \label{eqs:set_g}
  \underset{u \leftarrow \mu_{\delta}^k}{\Pr}[u \in \cG_b] = \underset{u \leftarrow \mu_{\delta}^k}{\Pr}[g(b, u_2, \dots, u_k) = 1]\notag\\
 \underset{\pi^{(k)}, \rho}{\Pr}[c \in \cG_b] = \underset{\pi^{(k)}, \rho}{\Pr}[g(b, c_2, \dots, c_k) = 1].
\end{align}
Let us fix the randomness $\pi_1$ to $\pi^*$. We use \eqref{eq:s_pi_b} and \eqref{eqs:set_g} to obtain
\begin{multline}
\label{eq:diff_s01}
\underset{u \leftarrow \mu_{\delta}^k}{\Pr}[u \in \cG_1] - \underset{u \leftarrow \mu_{\delta}^k}{\Pr}[u \in \cG_0] \\
 = \underset{\pi^{(k)}, \rho}{\Pr}[c \in \cG_1 \mid \pi_1 = \pi^*] - \underset{\pi^{(k)}, \rho}{\Pr}[c \in \cG_0 \mid \pi_1 = \pi^*] - (S_{\pi^*, 1} - S_{\pi^*,0})
\end{multline}
By monotonicity of $g$ it holds $\cG_0 \subseteq \cG_1$, and we write \eqref{eq:diff_s01} as
\begin{align}
  \label{eq:diff_s01_next}
  \underset{u \leftarrow \mu_{\delta}^k}{\Pr}[u \in \cG_1 \setminus \cG_0] = \underset{\pi^{(k)}, \rho}{\Pr}[c \in \cG_1 \setminus \cG_0 \mid \pi_1 = \pi^*] - (S_{\pi^*,1} - S_{\pi^*,0}).
\end{align}
Let us multiply both sides of \eqref{eq:diff_s01_next} by
\begin{align*}
\underset{
  \mathclap{
    \substack{r \\ x^* := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}}
    \\ (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{P^{(1)}} }}}
{\Pr}\mkern13mu [\Gamma_V(\widetilde{D}_2(x^*, r)) = 1]
 \mkern11mu / \underset{u \leftarrow \mu_{\delta}^k}{\Pr}[ u \in \cG_1 \setminus\cG_0],
\end{align*}
%
which yields
\begin{align}
\label{eq:pr_d_succ_0}
&\IndII\underset{
  \mathclap{
    \substack{r \\ x^* := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}} \\ (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{P^{(1)}} }}}
{\Pr}\mkern13mu[\Gamma_V(\widetilde{D}_2(x^*, r)) = 1] \notag\\
%
&\IndIII = \mkern13mu
  \underset{
    \mathclap{
      \substack{r \\ x^* := \langle P^{(1)}(\pi^*), D_1 (r) \rangle_{\mathit{trans}} \\ (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi^*), D_1 (r) \rangle_{P^{(1)}} }}}
  {\Pr}\mkern13mu[\Gamma_V(\widetilde{D}_2(x^*, r)) = 1]
  \underset{\pi^{(k)},\rho}{\Pr}[c \in \cG_1 \setminus \cG_0 \mid \pi_1 = \pi^*]
\frac{1}{\underset{u \leftarrow \mu_{\delta}^k}{\Pr}[ u \in \cG_1 \setminus \cG_0]}\notag\\
%
&\IndIIII - \mkern13mu
\underset{
  \mathclap{
  \substack{r \\ x^* := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}} \\ (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{P^{(1)}} }}}
{\Pr}\mkern13mu[\Gamma_V(\widetilde{D}_2(x^*, r)) = 1](S_{\pi^*,1} - S_{\pi^*,0})
\frac{1}{\underset{u \leftarrow \mu_{\delta}^k}{\Pr}[ u \in \cG_1 \setminus\cG_0]}.
\end{align}
Let us study the first summand of \eqref{eq:pr_d_succ_0}. First, we have
\begin{align}
  \label{eq:pr_gamma_v_0}
  \IndII &\underset{
    \mathclap{
      \substack{r \\
        x^* := \langle P^{(1)}(\pi^*), D_1 (r) \rangle_{\mathit{trans}} \\
        (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{P^{(1)}} }}}
  {\Pr}\mkern13mu[\Gamma_V(\widetilde{D}_2(x^*, r)) = 1] \notag\\
  &\IndI = \underset{
    \mathclap{
      \substack{r \\
        x^* := \langle P^{(1)}(\pi^*), D_1 (r) \rangle_{\mathit{trans}} \\
        (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{P^{(1)}} }}}
  {\Pr}[\Gamma_V(\widetilde{D}_2(x^*, r)) = 1 | \widetilde{D}_2(x^*,r) \neq \bot]
  \underset{\mathclap{\substack{r \\ x^* = \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}}}}}{\Pr}[\widetilde{D}_2(x^*,r) \neq \bot] \notag\\
  &\IndI \stackrel{(*)}{=}
  \underset{\pi^{(k)}, \rho}{\Pr}[c_1 = 1 \mid c \in \cG_1 \setminus \cG_0, \pi_1 = \pi^*]
  \underset{\mathclap{\substack{r \\ x^* = \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}}}}} {\Pr}[\widetilde{D}_2(x^*,r) \neq \bot]
\end{align}
where in $(*)$ we use the observation that $\widetilde{D}_2(x^*, r) \neq \bot$ happens if and only if $\widetilde{D}_2(x^*, r)$
finds $\pi^{(k)}$ such that $c \in \cG_1 \setminus \cG_0$. Furthermore, conditioned on $c \in \cG_1 \setminus \cG_0$
we have that $\Gamma_V(\widetilde{D}_2(x^*,r)) = 1$ happens if and only if $c_1 = 1$.
Inserting \eqref{eq:pr_gamma_v_0} to the numerator of the first summand of (\ref{eq:pr_d_succ_0}) yields
\begin{align}
  \label{ineq:start_for_case}
\IndI &\underset{
  \mathclap{
  \substack{r \\
    x^* := \langle P^{(1)}(\pi^*), D_1 (r) \rangle_{\mathit{trans}} \\
    (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{P^{(1)}} }}}
{\Pr}\mkern13mu[\Gamma_V(\widetilde{D}_2(x^*, r)) = 1]
\underset{\pi^{(k)},\rho}{\Pr}[c \in \cG_1 \setminus \cG_0 \mid \pi_1 = \pi^*] \notag\\
  &\IndI = \underset{\mathclap{\substack{r
      \\ x^* = \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}}}}}
  {\Pr}\mkern13mu[\widetilde{D}_2(x^*,r) \neq \bot]
  \underset{\pi^{(k)}, \rho}{\Pr}[c_1 = 1 \mid c \in \cG_1 \setminus \cG_0, \pi_1 = \pi^*]
  \underset{\pi^{(k)}, \rho}{\Pr}[c \in \cG_1 \setminus \cG_0 \mid \pi_1 = \pi^*].
\end{align}
We consider the following two cases. First, if $\Pr_{\pi^{(k)}, \rho}[ c \in \cG_1 \setminus \cG_0 \mid \pi_1 = \pi^*] \leq \frac{\epsilon}{6k}$ then
\begin{align}
  \label{ineq:case_0}
  \underset{\pi^{(k)}, \rho}{\Pr}[c_1 = 1 \mid c \in \cG_1 \setminus \cG_0, \pi_1 = \pi^*] \underset{\pi^{(k)}, \rho}{\Pr}[c \in \cG_1 \setminus \cG_0 \mid \pi_1 = \pi^*] \leq \frac{\epsilon}{6k}.
\end{align}
In case where $\Pr_{\pi^{(k)}, \rho}[c \in \cG_1 \setminus \cG_0 \mid \pi_1 = \pi^*] > \frac{\epsilon}{6k}$ the circuit $\widetilde{D}_2$ outputs $\bot$
if and only if it fails in all $\frac{6k}{\epsilon} \log(\frac{6k}{\epsilon})$ iterations to find $\pi^{(k)}$ such that $c \in \cG_1 \setminus \cG_0$
which happens with probability
\begin{align}
  \label{ineq:case_1}
\underset{
  \mathclap{
    \substack{
      r \\
      x^* := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}}}}}
{\Pr}[\widetilde{D}_2(x^*,r) = \bot]
\leq \Big(1 - \frac{\epsilon}{6k}\Big)^{\frac{6k}{\epsilon}\log(\frac{6k}{\epsilon})} \leq \frac{\epsilon}{6k}.
\end{align}
We conclude that in both aforementioned cases using \eqref{ineq:start_for_case}, \eqref{ineq:case_0} and \eqref{ineq:case_1} the following holds
\begin{align}
  \label{ineq:first_part}
  &\underset{
    \mathclap{
    \substack{r \\
      x^* := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}}}}}
  {\Pr}\mkern13mu[\widetilde{D}_2(x^*,r) \neq \bot]
  \underset{\pi^{(k)}, \rho}{\Pr}[c_1 = 1 \mid c \in \cG_1 \setminus \cG_0, \pi_1 = \pi^*]
  \underset{\pi^{(k)}, \rho}{\Pr}[c \in \cG_1 \setminus \cG_0 \mid \pi_1 = \pi^*] \notag\\
  &\IndII \stackrel{\hphantom{(\ref{eq:s_pi_b})}}{\geq}
  \underset{\pi^{(k)}, \rho}{\Pr}[c_1 = 1 \mid c \in \cG_1 \setminus \cG_0, \pi_1 = \pi^*]\underset{\pi^{(k)}, \rho}
  {\Pr}[c \in \cG_1 \setminus \cG_0 \mid \pi_1 = \pi^*] - \frac{\epsilon}{6k} \notag\\
  &\IndII \stackrel{\hphantom{(\ref{eq:s_pi_b})}}{=}
  \underset{\pi^{(k)}, \rho}{\Pr}[c_1 = 1 \land c \in \cG_1 \setminus \cG_0 \mid \pi_1 = \pi^*] - \frac{\epsilon}{6k} \notag\\
  &\IndII \stackrel{\hphantom{(\ref{eq:s_pi_b})}}{=}
  \underset{\pi^{(k)}, \rho}{\Pr}[g(c) = 1 \mid \pi_1 = \pi^*] -  \underset{\pi^{(k)}, \rho}{\Pr}[c \in \cG_0 \mid \pi_1 = \pi^*] - \frac{\epsilon}{6k} \notag\\
  &\IndII \stackrel{(\ref{eq:s_pi_b})}{=}
   \underset{\pi^{(k)}, \rho}{\Pr}[g(c) = 1 \mid \pi_1 = \pi^*] -  \underset{u \leftarrow \mu_{\delta}^{(k)}}{\Pr}[u \in \cG_0]  - S_{\pi^*,0} - \frac{\epsilon}{6k}.
\end{align}
We insert \eqref{ineq:first_part} into \eqref{eq:pr_d_succ_0} and calculate the expected value over $\pi^*$ which yields
\begin{align}
  \label{ineq:ex_pr_gamma}
\underset{
  \mathclap{
    \substack{\pi, r \\ x := \langle P^{(1)}(\pi), D_1(r) \rangle_{\mathit{trans}} \\ (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi), D_1(r) \rangle_{P^{(1)}} }}}
{\Pr}[\Gamma_V(\widetilde{D}_2(x, r)) = 1]
&\geq \mathbb{E}_{\pi^*}\left[\frac{\Pr_{\pi^{(k)}, \rho}[g(c) = 1 | \pi_1 = \pi^*]
  - \Pr_{u \leftarrow \mu_{\delta}^{(k)}}[u \in \cG_0] - \frac{\epsilon}{6k}}{\Pr_{u \leftarrow \mu_{\delta}^{(k)}}[u \in \cG_1 \setminus \cG_0]}\right] \notag\\
&- \mathbb{E}_{\pi^*}\Bigl[\Bigl(
\underset{\mathclap{
  \substack{r \\ x^* := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}} \\ (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{P^{(1)}} }}}
{\Pr}[\Gamma_V(\widetilde{D}_2(x^*, r)) = 1](S_{\pi^*,1} - S_{\pi^*,0})
 + S_{\pi^*,0}\Bigr)
\frac{1}{\underset{u \leftarrow \mu_{\delta}^k}{\Pr}[ u \in \cG_1 \setminus\cG_0]}\Bigr].
\end{align}
We now show that if $\widetilde{\Gen}$ does not recurse, then the majority of estimates is low almost surely.
Let us assume that
\begin{align}
\underset{\pi}{\Pr}\left[\left(S_{\pi,0} \leq (1 - \frac{1}{2k})\epsilon\right) \land \left( S_{\pi,1} \leq (1-\frac{1}{2k})\epsilon\right)\right] < 1 - \frac{\epsilon}{6k},
\end{align}
then $\widetilde{\Gen}$ recurses almost surely, because the probability that
$\widetilde{\Gen}$ does not find $\widetilde{S}_{\pi, b} \geq (1-\frac{3}{4k})\epsilon$ in all of the $\frac{6k}{\epsilon}n$ iterations is at most
\begin{align*}
  \Bigl(1 - \frac{\epsilon}{6k}\Bigr)^{\frac{6k}{\epsilon}n} \leq e^{-n}
\end{align*}
almost surely, where we used Lemma \ref{lemma:surplus_estimate}.
Therefore, under the assumption that $\widetilde{\Gen}$ does not recurse with high probability it holds
\begin{align}
\underset{\pi, \rho}{\Pr}\left[\left(S_{\pi,0} \leq (1 - \frac{1}{2k})\epsilon\right) \land \left( S_{\pi,1} \leq (1-\frac{1}{2k})\epsilon\right)\right] \geq 1 - \frac{\epsilon}{6k}.
\end{align}
Let us define a set
\begin{align}
  \cW = \left\{ \pi :  \left(S_{\pi,0} \leq (1 - \frac{1}{2k})\epsilon\right) \land \left( S_{\pi,1} \leq (1-\frac{1}{2k})\epsilon \right) \right\}.
\end{align}
Additionally, let $\overline{\cW}$ denote the complement of $\cW$.
We bound the numerator of the second summand in (\ref{ineq:ex_pr_gamma})
\begin{align}
  \label{ineq:second_eq}
&\mathbb{E}_{\pi^*}\Big[ S_{\pi^*,0}
\mkern23mu
+
\mkern23mu
\underset{
  \mathclap{
  \substack{r \\ x^* := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}}
    \\ (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi^*), D_1 (r) \rangle_{P^{(1)}} }}}
{\Pr}\mkern13mu[\Gamma_V(\widetilde{D}_2(x^*, r)) = 1]
(S_{\pi^*,1} - S_{\pi^*,0})\Big] \notag\\
%
&\IndII = \mathbb{E}_{\pi^*}\Bigl[ S_{\pi^*,0}
\mkern23mu + \mkern23mu
\underset{
  \mathclap{
  \substack{r \\ x^* := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}}
    \\ (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi^*), D_1 (r) \rangle_{P^{(1)}} }}}
{\Pr}\mkern13mu[\Gamma_V(\widetilde{D}_2(x^*, r) = 1]
  (S_{\pi^*,1} - S_{\pi^*,0}) \bigm| \pi^* \in \overline{\cW}\Bigr] \Pr_{\pi^*}[\pi^* \in \overline{\cW}]\notag\\
&\IndIII +  \mathbb{E}_{\pi^*}\Bigl[ S_{\pi^*,0} \mkern13mu + \mkern13mu
\underset{
  \mathclap{
  \substack{r \\ x^* := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}}
    \\ (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi^*), D_1 (r) \rangle_{P^{(1)}} }}}
{\Pr}\mkern13mu[\Gamma_V(\widetilde{D}_2(x^*, r)) = 1]
(S_{\pi^*,1} - S_{\pi^*,0})  \bigm| \pi^* \in \cW\Bigr] \Pr_{\pi^*}[\pi^* \in \cW] \notag\\
&\IndII \leq \frac{\epsilon}{6k} + \mathbb{E}_{\pi^*}\Bigl[ S_{\pi^*,0} \mkern23mu + \mkern23mu
\underset{
  \mathclap{
  \substack{r \\ x := \langle P^{(1)}(\pi^*), D_1(r) \rangle_{\mathit{trans}}
    \\ (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi^*), D_1 (r) \rangle_{P^{(1)}} }}}
{\Pr}\mkern13mu\big[\Gamma_V(\widetilde{D}_2^{\widetilde{C}}(x^*, r)) = 1\big]
\big(\bigl(1 - \frac{1}{2k}\bigr)\epsilon - S_{\pi^*,0}\big)  \bigm| \pi^* \in \cW \Bigr] \notag\\
% \Pr_{\pi^*}[\pi^* \in \cW] \notag\\
&\IndII \leq \frac{\epsilon}{6k} + (1 - \frac{1}{2k})\epsilon = (1 - \frac{1}{3k}) \epsilon.
\end{align}
Finally, we insert \eqref{ineq:second_eq} into \eqref{ineq:ex_pr_gamma} which yields
\begin{align*}
  \IndI
\underset{
  \mathclap{
  \substack{\pi, \rho \\ x := \langle P^{(1)}(\pi), D_1(\rho) \rangle_{\text{trans}}
    \\ (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi), D_1 (\rho) \rangle_{P^{(1)}} }}}
{\Pr}\big[\Gamma_V(\widetilde{D}_2(x, \rho)) = 1\big]
&\geq \underset{\pi^*}{\mathbb{E}}\left[\frac{{\Pr}_{\pi^{(k)}, \rho}[g(c) = 1 \mid \pi_1 = \pi^*] -
{\Pr}_{u \leftarrow \mu_{\delta}^{k}}[u \in G_0] - (1 - \frac{1}{6k})\epsilon} {\Pr_{u \leftarrow \mu_{\delta}^{k}}[u \in \cG_1 \setminus \cG_0]}\right] \notag.
 \end{align*}
 From the assumptions of Lemma \ref{lemma:sec_amp_for_p_hash} it follows that
 \begin{align}
   \label{eq:lemma_assum}
   \Pr_{\pi^{(k)}, \rho} [g(c) = 1] \geq \Pr_{u \leftarrow \mu_{\delta}^{(k)}}[g(u) = 1] + \epsilon.
 \end{align}
We observe that
\begin{align}
  \label{eq:gu_rel}
\underset{u \leftarrow \mu_{\delta}^k}{\Pr}[g(u) = 1]
&= \Pr[u \in \cG_0 \lor ( u \in \cG_1 \setminus \cG_0 \land u_1 = 1)] \notag\\
&= \Pr[u \in \cG_0] + \delta \Pr[u \in \cG_1 \setminus \cG_0].
\end{align}
 Using \eqref{eq:gu_rel} and \eqref{eq:lemma_assum} we obtain
 \begin{align}
   \label{eq:proof_final}
   \IndI
\underset{
  \mathclap{
  \substack{\pi, \rho \\ x := \langle P^{(1)}(\pi), D_1(\rho) \rangle_{\text{trans}}
    \\ (\Gamma_V, \Gamma_H) := \langle P^{(1)}(\pi), D_1 (\rho) \rangle_{P^{(1)}} }}}
{\Pr}\mkern13mu[\Gamma_V(\widetilde{D}_2(x, \rho)) = 1]
 &\stackrel{\hphantom{\eqref{eq:gu_rel}}}{\geq} \frac{ {\Pr}_{u \leftarrow \mu_{\delta}^{k}}[g(u) = 1] + \epsilon -
 \Pr_{u \leftarrow \mu_{\delta}^{k}}[u \in \cG_0] - (1 - \frac{1}{6k})\epsilon} {\Pr_{u \leftarrow \mu_{\delta}^{k}}[u \in \cG_1 \setminus \cG_0]} \notag\\
 &\stackrel{\eqref{eq:gu_rel}}{\geq} \frac{\epsilon + \delta\Pr_{u \leftarrow \mu_{\delta}^{k}}[u \in \cG_1 \setminus \cG_0] - (1 - \frac{1}{6k})\epsilon}
{\Pr_{u \leftarrow \mu_{\delta}^{k}}[u \in \cG_1 \setminus \cG_0]} \geq \delta + \frac{\epsilon}{6k}.
\end{align}
Clearly, the running time of $\widetilde{\Gen}$ is bounded by some polynomial $p(k, \frac{1}{\epsilon}, n)$ with oracle calls.
Furthermore, the algorithm $\widetilde{\Gen}$ outputs a circuit $\widetilde{D}$ such that it satisfies with probability at least $1 - \p(k, \frac{1}{\epsilon}, n) \cdot 2^n$
the statement of Lemma \ref{lemma:sec_amp_for_p_hash}. This concludes the proof of Lemma~\ref{lemma:sec_amp_for_p_hash}.
\end{proof}
%
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../master"
%%% End:
